\documentclass{clean_CV}

% Add a BibTeX-style file encoding all of your publications to include here. You can export this from Zotero. Only include
% publications you want to appear here!
\addbibresource{publications.bib}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=black,
}
\usepackage{multicol, multirow, ulem, array}
\raggedcolumns
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}

\author{Jesper Böjeryd}
%\renewcommand{\today}{November 20, 2023}

\newcommand{\datetabspace}{5.5em}

\geometry{includeheadfoot, margin=0.6in, bottom=0.3in, top=-0.1in}
\fancyhfoffset[r]{0.0in} % I don't know why but this makes the footer align with the new margins

\begin{document}

\begin{tabular}
    {@{}p{0.34\textwidth}@{}R{0.30\textwidth}@{}R{0.36\textwidth}@{}}
    \multirow{3}{*}[3.7pt]{\Huge Jesper Böjeryd}
    & +1 (310) 775-3781
    & \url{jesper.hw.bojeryd@gmail.com} \\
    & \url{www.jesperbojeryd.se}
    & \url{www.github.com/bojeryd91} \\
    & \multicolumn{2}{r@{}}{\url{www.linkedin.com/in/jesperbojeryd}}
\end{tabular}

\section{Summary}
\eatvspace
\begin{multicols}{3}
    \textbf{Versatile researcher:} 10 years of experience in data collection, analysis, and presentation using financial, health, credit, corporate, realtor, and admin data. Raised \$533,000 in research grants.

    \columnbreak

    \textbf{Technical skills:} I combine my engineering training and economic analysis to produce code tailor to solving complex problems.

    \columnbreak
    
    \textbf{Collaborative:} I manage projects with collaborators in multiple countries and institutions, and train and mentor researcher assistants and PhD students.
\end{multicols}


%\textbf{Programming skills:} Stata, Julia (parallel computing), R, Matlab, Python, Java. \quad (\uline{\href{https://github.com/bojeryd91}{Link to \faGithub{}}})

%\textbf{Data experience:} 10 years experience in collecting, cleaning, and analyzing large, mixed panel datasets. Inter-research team collaboration regarding a data server and meeting with data providers to specify deliveries.
    
%\textbf{Quantitative modeling:} Asset pricing, solving and simulating household finance/wealth models

%\textbf{Personal qualities:} Detail-oriented, self-disciplined team player used to collaborate across teams



%\section{Research experience {\normalsize (\uline{})}}
\section{Professional experience% {\normalsize (\texorpdfstring{\protect\uline{\href{https://www.jesperbojeryd.se/research}{link to complete list}}}{for a complete list, see link}})
}

\position{Postdoctoral Researcher, Department of Economics, Stockholm University}{2024--present}

\begin{itemize}
    \item Submitted \textit{The housing wealth effect: Quasi-experimental evidence} -- R\&R at JME.
    \item Managed a new micro-data-intensive project combining data from both private and public providers.
    \item Developed and taught with short notice a master-level course in solving quantitative macroeconomic models using \texttt{MATLAB}/Dynare.
\end{itemize}

\medskip

\position{Guest Researcher and Ph.D. Intern, Norges Bank}{2022--present}
\begin{itemize}
    \item Conducted a co-authored project with central-bank researchers studying household-level expenditures in response to shocks to home prices. %We use the near-universe of digital payments in Norway combined with rich administrative data using an instrumental-variable approach.
    \item Presented work for the Norges Bank Research Department and policymakers.
    \item Developed memory-effective routines and data-cleaning scripts for Norway's Central Bank. %\quad
    %Researchers suffered from freezing servers due to limited memory access when many would clean data
\end{itemize}

\medskip

\position{Ph.D., University of California, Los Angeles}{2018--2024}

\begin{itemize}
    \item Wrote my dissertation consisting of four empirical studies
    %
    \begin{itemize}
        \item \textit{Empirical methods used:} Standard and continuous difference-in-differences, instrumental variable regressions (2SLS and two-sample 2SLS).
        %
        \item \textit{Structural methods used:} General equilibrium, life-cycle models.
        %
        \item \textit{Data:} TRACE (High-frequency, over-the-counter U.S. corporate bond data); Compustat (US financial data); Swedish and Norwegian realtor data; Swedish and Norwegian administrative data (individual-level tax and other data. Very comprehensive).
    \end{itemize}
    %
    \item Taught extensively at the undergraduate and graduate levels (see below).
    %
    \item Collaborated with Stata Corp debugging and resolving a bug. Fix shipped in an official Stata 17 update. Likewise for the user-written \texttt{boottest}.
\end{itemize}


\iffalse
\medskip

\position{Thomas J. Sargent Dissertation Fellow at the Federal Reserve Bank of San Francisco}{2023}


\begin{itemize}
    \item Received fellowship and access to the bank's researchers to continue research on my dissertation.
    \item Presented solo-authored work twice to the research department and discussed research with Fed and guest researchers.
\end{itemize}
\fi

\medskip

\position{Research Assistant at The Riksbank and the Swedish House of Finance}{2015--2018}

\begin{itemize}
    \item Collected and analyzed corporate and household credit data, health data and wrote data scraper (\texttt{Python}).
    \item Contributed to six published articles on credit use, health economics, and labor economics.
    %\begin{itemize}
    %    \item \uline{\href{https://academic.oup.com/rfs/article/31/6/2005/4822045}{The Labor Market Effects of Credit Market Information}}
    %    \item \uline{\href{https://academic.oup.com/rfs/article/34/5/2608/5893490}{Impulsive Consumption and Financial Wellbeing}}
    %    \item \uline{\href{https://link.springer.com/article/10.1007/s11238-021-09815-2}{Scarcity and Consumers' Credit Choices}}
    %    \item \uline{\href{https://onlinelibrary.wiley.com/doi/10.1111/jmcb.12736}{Bad Times, Good Credit}}
    %    \item \uline{\href{https://www.science.org/doi/full/10.1126/sciadv.aba1551}{ADHD, Financial Distress, and Suicide in Adulthood: A Population Study}}
    %    \item \uline{\href{https://www.sciencedirect.com/science/article/pii/B9780128135242000056}{Rationality in the Consumer Credit Market}}
    %\end{itemize}
    \item Managed data server and junior research assistants. Collaborated across research teams.
\end{itemize}

\medskip

% Clarify connection to FINANCE
\position{Master thesis at KTH Royal Institute of Technology}{2015}

\begin{itemize}
    \item Performed independent research of simulation methods in molecular dynamics/systems of SDEs in \texttt{Matlab}, applying skills from the financial mathematics track. %\quad (\uline{\href{https://www.diva-portal.org/smash/get/diva2:808180/FULLTEXT01.pdf}{Link to thesis}})
    \item Taught at the undergraduate level.
    \item Trained in \texttt{Python}, \texttt{Java}, and \texttt{COMSOL}.
\end{itemize}

\section{Teaching experience}
\eatvspace
\begin{multicols}{2}
Stockholm University, lecturer
\begin{itemize}
    \item Quantitative Macroeconomics, EC7218
\end{itemize}

\medskip

University of California, Los Angeles, TA
\begin{itemize}
    \item Statistics for Economists, Econ 41
    \item Financial Markets and Financial Institutions, Econ 106M
    \item Macroeconomic Theory, Econ 102
    \item Year 1 PhD Macroeconomics, Econ 202A
    \item Corporate Finance, Econ 106F
\end{itemize}

\medskip

KTH Royal Institute of Technology, TA
\begin{itemize}
    \item Real and Numerical Analysis
    \item Statistics and Probability Theory
\end{itemize}
\end{multicols}

\section{Education}

\position{Ph.D., Economics}{2018--2024}

University of California, Los Angeles, USA

Specialization: Macroeconomics and Finance

\medskip

\position{M.Sc., Engineering Physics/Applied and Computational Mathematics}{2010--2015}

KTH Royal Institute of Technology, Stockholm, Sweden

Specialization: Financial Mathematics (\textit{Arbitrage theory, derivative pricing, time series analysis})


\section{Research papers}
WP: \textit{Should I Stay of Should I Go? The Role of Housing in Understanding Limited Inter-Regional Worker Mobility}

\smallskip

SSRN WP: \textit{The Housing Wealth Effect: Quasi-Experimental Evidence} -- submitted \\ {with Dany Kessel, Björn Tyrefors, and Roine Vestman

\smallskip

\textit{What Do 12 Billion Card Transactions Say About House Prices and Consumption?} \\
with Knut Are Aastveit, Magnus Gulbrandsen, Ragnar Juelsrud, Kasper Roszbach

\smallskip

UCLA Ziman Center for Real Estate WP: \textit{Heterogeneous Effects of QE on Corporate Bonds and Firm Outcomes} \quad
with Adam Baybutt

\smallskip

Thesis: \textit{Long Time Integration of Molecular Dynamics at Constant Temperature with the Symplectic Euler Method}

\smallskip

For drafts, see \url{www.jesperbojeryd.se/research}.

\section{Additional information}

\textbf{Languages:} English (full professional proficiency), Swedish (native).

\smallskip

\textbf{Programming skills:} Stata, Julia (parallel computing), R, Matlab, Python, Java. %\quad (\uline{\href{https://github.com/bojeryd91}{Link to \faGithub{}}})

\smallskip

\textbf{Awards:} Thomas J. Sargent Dissertation Fellow at the FRB of San Francisco, Research grants (\$533,000), Best pro-seminar presentation 2023 (UCLA), Teaching award (UCLA), Swedish Homeguard's bronze medal.

\end{document}
