\documentclass[letterpaper,10pt]{article}
\pagenumbering{gobble}
\usepackage[utf8]{inputenc}
\usepackage{titlesec, hyperref}

% A test

% Change behavior of and spacing around sections and paragraphs
\usepackage{titlesec}
\titleformat{\section}{\normalfont\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.4pt]\vspace{3pt}}]
\titlespacing\section{0pt}{6pt}{0pt}
\titlespacing\paragraph{0pt}{6pt}{0pt}

\footskip=0pt
\setlength{\parindent}{0pt}

\usepackage[top=0.7in,left=1in,right=1in, bottom=1.5in,marginparwidth=1.1in]{geometry}

% A command with bold text and some additional space before
\newcommand{\bold}[1]{\ifhmode\hspace{6pt}\fi\textbf{#1:}}

\begin{document}
\begin{center}
{\Large \textbf{Curriculum vitae -- Jesper Böjeryd}}\\[3pt]
Born: 1991 \hspace{6pt} Nationality: Swedish \hspace{6pt} Email: bojeryd91@gmail.com \\
Phone: +1 (310) 775-3781 \hspace{6pt} Address: 2014 S Bentley Avenue, Los Angeles, 90025, CA, USA \\
\url{www.jesperbojeryd.se}
\end{center}

\section*{Education}
\paragraph{2018--Exp. Jun 2024, Econ Ph.D. program}\hfill University of California, Los Angeles, USA\\
C.Phil, M.A., fields: Macroeconomics, Asset pricing\\
Committee: \href{https://www.leeohanian.com/}{Lee Ohanian (Main advisor)}, \href{https://sites.google.com/site/andyatkeson/}{Andy Atkeson}, \href{https://sites.google.com/site/kyleherkenhoff/}{Kyle Herkenhoff}, \href{https://sites.google.com/site/pierreolivierweill/}{Pierre-Olivier Weill}

\paragraph{2010--2015, Engineering physics,}\hfill Royal Institute of Technology, Sweden\\
M.Sc.Eng, M.Sc, and B.Sc, concentration: Applied and computational mathematics\\
Master thesis: \href{https://www.diva-portal.org/smash/record.jsf?pid=diva2\%3A808180&dswid=-588}{\texttt{Long time integration of mole\-cular dynamics at constant  temperature with the symplectic Euler method}}, supervised by  Anders Szepessy

%The thesis studies a numerical algorithm to solve a class of problems in statistical physics. I investigate how to efficiently integrate functions over the whole state space for indefinite time. I studied articles on the topic, set up experiments, implemented methods, and evaluated and presented the results. The algorithm is applied to three different experiments and evaluated against alternative methods found in the literature.

\paragraph{Mar--Jun 2013, Exchange semester}\hfill KAIST, Republic of South Korea\\
Studied individual courses and wrote my bachelor thesis.


\paragraph{Spring 2010, Individual course}\hfill Karlstad University, Sweden\\
Elementary Algebra. This was a unique one-year project to encourage talented students to study college-level mathematics during my senior year in high school

\section*{Work experience}
\paragraph{2019--present, Teaching assistant}\hfill UCLA\\
I have taught the courses \emph{Statistics for economists}, and \emph{Financial markets and financial institutions}. Before every session I identify the concepts students are most unfamiliar with, and focus on those and connect them to their existing knowledge. I encourage a continuous dialogue by involving students in class and using OHs.

\paragraph{2015--2017, summer 2019, Research assistant}\hfill The Riksbank and Swedish House of Finance\\
As an RA for Marieke Bos and Peter van Santen, I have participated in every part of a research project. I sat in on out-of-house meetings to collect new data; planned, implemented, and presented data analysis using panel data econometrics; and discussed paper drafts and suggested improvements. I also held a one-day course in basic MATLAB programming for the Riksbank's forecasting division and provided general help in econometrics and programming to colleagues.

\paragraph{Periodically 2014--2015, Teaching assistant}
\hfill Royal Institute of Technology\\
Selection of courses: \emph{Probability theory and statistics}; \emph{Mathematical and numerical analysis}. I graded students based on finals, reports, and oral presentations, and tutored them by feedback and answering questions during lab sessions.

\section*{Language \& computer skills}
\bold{Native} Swedish \bold{Fluent} English \\
\bold{Advanced} MATLAB, Stata, \LaTeX; \bold{Intermediate} R; \bold{Beginner} Python, Java, Julia, Github

\section*{Awards \& fellowships}
\bold{2020} Ziman Center’s UCLA Rosalinde and Arthur Gilbert Program (UCLA), European Studies Fellowship (UCLA), Summer Graduate Fellowship (UCLA), Graduate Summer Research Mentorship program (UCLA) \bold{2019} Frida och A O Ringqvists minnesfond (Karlstad) \bold{2018} Ernst O Ek's stipendiefond (Sverige-Amerika Stiftelsen) \bold{2015}
The Fellows of KTH Scholarship Fund (Kamratstipendiefonden) \bold{2012} Winner of EBEC Stockholm and representative of KTH at the Nordic finals (BEST) \bold{2011} The Homeguard's bronze medal \emph{Awarded for my diligent work as member of the Skaraborg Homeguard Marching Band.}

\section*{Extra-curricular activities} 
\bold{2015 and 2018} Volunteer at Mattecentrum as additional support in mathematics for high school students \bold{2000--2018} Musician, playing the trombone in several orchestras. \href{https://www.youtube.com/watch?v=nn6dDYi3AFg}{\texttt{Link to recording!}}
\iffalse
\iffalse
\emph{Several elected positions} in my division of KTH Student association, including:
\begin{lista2}
\emph{Treasurer} for a committee, \\
\emph{Producer} (head) for a play involving 100 people.  \bold{2011--2015}
\end{lista2}
\fi
\emph{Musician}, playing the trombone in several orchestras.% Lately mainly in symphonic orchestras.
\bold{2000--2018}

%\section{REFERENCES}
%\emph{Will be provided on request.}
%\iffalse
%{\setlength{\topsep}{-\parskip}%
%\setlength{\partopsep}{0pt}%
%\tabbing
%Anders Szepessy,\=\hspace*{6pt}\= former supervisor, \= +46 8 790 74 94,\hspace*{6pt} \= szepessy@kth.se\\
%Peter van Santen,\>\> former employer,    \> +46 8 787 05 69, \> \parbox[t][2em][t]{3.5cm}{peter.van.santen @riksbank.se}\\
%Marieke Bos, \>                  \> employer,          \> +46 73 573 74 61, \> Marieke.Bos@hhs.se
%\endtabbing}
%\fi
\fi
\end{document}